A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2022-06-11 kobakian-cook.Rmd
Update kobakian-cook.Rmd

The Australian Cancer Atlas is an online, interactive display of Australian cancer statistics in each of the Statistical Areas at Level 2 (SA2s), used by the @abs2011. The estimated standardised incidence ratios (SIRs) of thyroid cancer 
for females was downloaded from the Australian Cancer Atlas and presented in Figure \@ref(fig:choro), a choropleth map that uses colour to display the distribution. The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states. The SA2s on the east coast around Brisbane and in northern New South Wales stand out as more orange and red. However, this display neglects the vast amount of Australia residents living in the densely populated capital cities.

>>>>

The Australian Cancer Atlas is an online, interactive display of Australian cancer statistics in each of the Statistical Areas at Level 2 (SA2s), used by the @abs2011. The estimated standardised incidence ratios (SIRs) of thyroid cancer 
for females was downloaded from the publicly accessible Australian Cancer Atlas website and presented in Figure \@ref(fig:choro), a choropleth map that uses colour to display the distribution. The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states. The SA2s on the east coast around Brisbane and in northern New South Wales stand out as more orange and red. However, this display neglects the vast amount of Australia residents living in the densely populated capital cities.
